Automated Formal Synthesis of Provably Safe Digital Controllers for Continuous Plants

### 2019-07-23 automatica/paper.tex
paper

We consider models of physical plants expressed as ordinary differential
equations, which we assume to be controllable~\cite{Astrom08}: 
%
\begin{align}
\label{eq:ode1}
\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), 
\end{align}
%
where 
$\vec{x} \in \mathbb{R}^n$,  
$\vec{u} \in \mathbb{R}^p$, 
$\mat{A} \in \mathbb{R}^{n \times n}$, 
$\mat{B} \in \mathbb{R}^{n \times p}$,
and $t \in \mathbb R_0^+$ denotes continuous time. 
%$\mat{A}$ and $\mat{B}$ are matrices that fully characterize the dynamics of the continuous plant,
We denote with $x(0)$ the model initial condition, which can be non-deterministic.  
\rev{ We assume full observability of the states of the model, namely the output states correspond with the model variables.  }

@@

\rev{ Recall that the states of the model are fully accessible (namely, observable). } 
We consider state feedback control architectures, 
where $u_k$ (notice we work with the discretized signal) is $u_k = r_{k} - K x_k$. 
Here $K \in \mathbb{R}^{p \times n}$ is a state-feedback gain matrix, 
and $r_{k}$ is a reference signal (again digital). 
We will assume $r_k=0$ \rev{(meaning that the reference signal is just the origin)}, thus obtaining the closed-loop model 
$\vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k$.

>>>>

We consider models of physical plants expressed as ordinary differential
equations, which we assume to be controllable~\cite{Astrom08}: 
%
\begin{align}
\label{eq:ode1}
\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), 
\end{align}
%
where 
$\vec{x} \in \mathbb{R}^n$,  
$\vec{u} \in \mathbb{R}^p$, 
$\mat{A} \in \mathbb{R}^{n \times n}$, 
$\mat{B} \in \mathbb{R}^{n \times p}$,
and $t \in \mathbb R_0^+$ denotes continuous time. 
%$\mat{A}$ and $\mat{B}$ are matrices that fully characterize the dynamics of the continuous plant,
We denote with $x(0)$ the model initial condition, which can be non-deterministic.  
\rev{ We assume full observability of the states of the model, namely the output states correspond with the model variables, which we can thus fully access.  }

@@

\rev{ Recall that the states of the model are fully accessible (namely, observable). } 
We consider state feedback control architectures, 
where $u_k$ (notice we work with the discretized signal) is $u_k = r_{k} - K x_k$. 
Here $K \in \mathbb{R}^{p \times n}$ is a state-feedback gain matrix, 
and $r_{k}$ is a reference signal (again digital). 
We will assume $r_k=0$ \rev{(meaning that the reference signal is just a zero signal)}, thus obtaining the closed-loop model 
$\vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k$ \rev{with the origin as its equilibrium point}.
